Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?

### 2016-09-26 ms/ms.tex
minor changes

Based on inequality (\ref{inequality}), \citet{cramer} defines efficiency of unbiased 
estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
achievable by an estimator is unity. The closer the root-mean-squared 
to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
the estimator is.

@@

\section{Centroiding methods}\label{sec:method}
\begin{description}

@@

An optimal stellar centroiding algorithm must saturate---or come close to saturating---the fundamental Cram\'{e}r-Rao lower 
bound. That is, in all ranges of background noise level, size, radial light profile,
and shape, it must preserve information about the centroids of stars. In practice however,
this is only achievable when we have a reasonably good estimate of the PSF. Since we do not always 
know the exact PSF profile, we must make use of approximate centroiding algorithms. In this work, we
studied how close we get to saturating the CRLB with an approximate method acting on relatively low 
signal-to-noise ratio, unsaturated stars.

>>>>

Based on inequality (\ref{inequality}), \citet{cramer} defines efficiency of unbiased 
estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
achievable by an estimator is unity. The closer the RMSE to the CRLB, 
the more information about the parameter of interest is preserved, and thus the more efficient 
the estimator is.

@@

\section{Centroiding methods}\label{sec:method}

In this section, we briefly discuss the approximate and the non-approximate centroiding methods considered in this 
study.

\begin{description}

@@

An efficient stellar centroiding algorithm must saturate---or come close to saturating---the fundamental 
Cram\'{e}r-Rao lower bound. That is, in all ranges of background noise level, size, radial light profile,
and shape, it must preserve information about the centroids of stars. In practice however,
this is only achievable when we have a reasonably good estimate of the PSF. Since we do not always 
know the exact PSF profile, we must make use of approximate centroiding algorithms. In this work, we
studied how close we get to saturating the CRLB with an approximate method acting on relatively low 
signal-to-noise ratio, unsaturated stars.
